# Libraries

```{r}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(Rtsne)
library(reshape2)
```

# Q1: Diamonds Dataset

Among all numerical variables of the diamonds dataset, which one has the strongest correlation with the price?

```{r}
diamonds

cor_price <- diamonds %>% select(carat, depth, table, price, x, y)
cor(cor_price) ["price", ]
```

[Answer 1]{.underline}: Carat

# Q2: Tree growth

Produce a plot using the built-in **Orange** dataset that tracks the growth of five orange trees as a function of their age (in days). The plot should look at the circumference of these trees throughout their age - for each of the five orange trees.

```{r}
orange <- Orange
orange

growth <- ggplot(data = orange, aes(x = age, y = circumference, color=Tree)) + geom_path() +geom_point()
growth + labs(title = "Orange tree growth")
```

# Q3: Nested Plots

Produce a visualization using the built-in **Diamonds** dataset, that graphs the depth and price for all 5 cuts of diamonds (fair, good, very good, premium, and ideal).

```{r}
ggplot(diamonds, aes(x=depth, y=price, color = as.factor(cut))) + geom_point() + facet_grid(rows=vars(cut))      
```

# Q4: Raster Plots

Create a raster plot of the built-in dataset **volcano**.

```{r}
volcano <- melt(volcano)

ggplot(volcano, aes(x=Var1, y=Var2)) + geom_raster(aes(fill=value))
```

# Q5: Iris

Produce a visualizatiion of the count and sepal length of the three different species in the built-in **Iris** dataset.

```{r}
iris <- as.data.frame(iris)

ggplot(iris, aes(x = Sepal.Length, fill=as.factor(Species))) +
  geom_dotplot(binwidth = 0.1) + coord_flip()
```

# Q6: Dimensionality Reduction

The builtin dataset **state.x77** contains information about all 50 US states. Do a 2D PCA projection of them and answer: what state is most similar to Mississippi?

```{r}
state.x77

pca <- as.data.frame(prcomp(state.x77, scale = TRUE) $x)
pca

ggplot(pca, aes(x = PC1, y = PC2, label = rownames(pca))) + geom_point() + geom_text(size = 2)
```

[Answer]{.underline}: South Carolina
